\textbf{Designing a Virtual Security Management Layer for Cloud Content}

### 2016-01-29 tex/paper.tex
Added result of adding indices

\paragraph{GET requests}
\par
To be able to determine what is the bottleneck of the back-end three different types of \textit{GET
requests} are performed. The first one tries to maximise the number of requests that spray-can (HTTP
server) can handle with the given specifications and therefore the server just returns 200 (OK). The
second request requests the simplest API call which involves getting all currently stored projects
from the MongoDB instance. As this involves the server answering with some payload, the third
request is simply the same amount of static payload as the second request but without involving any
connections to MongoDB.
\par
The typical requests with Wrk in this work will look similar to this:
\begin{lstlisting}[frame=single]
wrk -t100 -c100 -d10s http://perius:8000/ok
\end{lstlisting}
where -t100 means that it uses 100 threads, -c100 that it emulates 100 clients requesting over and
over and -d100s is the amount of time that the load test will run, in this case 100 seconds.

@@

\textbf{POST requests}

\fix Add graphs of load testing etc

>>>>

\paragraph{GET requests}\mbox{}\\
To be able to determine what is the bottleneck of the back-end three different types of \textit{GET
requests} are performed. The first one tries to maximise the number of requests that spray-can (HTTP
server) can handle with the given specifications and therefore the server just returns 200 (OK). The
second request requests the simplest API call which involves getting all currently stored projects
from the MongoDB instance. As this involves the server answering with some payload, the third
request is simply the same amount of static payload as the second request but without involving any
connections to MongoDB.
\par
The typical requests with Wrk in this work will look similar to this:
\begin{lstlisting}[frame=single]
wrk -t100 -c100 -d10s http://perius:8000/ok
\end{lstlisting}
where -t100 means that it uses 100 threads, -c100 that it emulates 100 clients requesting over and
over and -d100s is the amount of time that the load test will run, in this case 100 seconds.

@@

\par
Another simple optimisation that was added was indices on the parent id's, which are heavily queried
when building the project trees.

\begin{lstlisting}[label=INDEXREQUEST,caption=Result of indexed project tree requests]
wrk -t100 -c100 -d100s 
  http://perius:8000/projects/56a5f...

Running 10s test @ http://perius:8000/projects/56a...
  100 threads and 100 connections
  Thread Stats   Avg      Stdev     Max   +/- Stdev
    Latency    47.27ms    3.03ms  86.54ms   93.79%
    Req/Sec    21.12      3.50    60.00     87.51%
  21271 requests in 10.10s, 9.76MB read
Requests/sec:   2105.82
Transfer/sec:      0.97MB
\end{lstlisting}

After adding indices, the building of the project tree was able to finish 50 times faster and the
server was able to serve 2100 requests/s, see Listing~\ref{INDEXREQUEST}.

\paragraph{POST requests}\mbox{}\\
Two different POST requests will be tested, creation of containers and creation of content together
with file uploads.

\begin{lstlisting}[label=CONTAINERPOSTREQUEST,caption=Result of container creation]
wrk -c24 -t12 -d4s -s post.lua 
  http://perius:8000/projects/56ab.../containers

Running 4s test @ 
  http://perius:8000/projects/56ab.../containers
  12 threads and 24 connections
  Thread Stats   Avg      Stdev     Max   +/- Stdev
    Latency     5.92ms    1.25ms  19.58ms   91.67%
    Req/Sec   339.86     76.68     1.28k    95.65%
  16357 requests in 4.10s, 5.04MB read
Requests/sec:   3990.12
Transfer/sec:      1.23MB
\end{lstlisting}

As can be seen in Listing~\ref{CONTAINERPOSTREQUEST} the server can handle around 4000 container
POST requests per second. The problem that this test resulted in was not the amount of containers
that could be posted, but rather loading all those containers in the interface or API afterwards.
When requesting the project that the containers were posted to the web server timed out the request,
as it took too long for the back-end to build the project tree. In this work, the web server wont 
be configured to accept longer data processing time, as trees as large as this for a single project
wont be used in production.

\par
As the project tree is built by querying documents parent id one optimisation that could be done was
to create an index of the documents parent ids. This drastically improved the size of the tree that
the server was able to handle within the time out, going from being able to handle 4000 documents to
at least 50000 documents, which the browser instead will have problems displaying represented in the 
UI without lag.
